Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Finished first draft.  Sending to co-authors for first round edits.

XXXXX

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL

>>>>

A stacked target of natural Nb, Cu, and Al thin foils were irradiated by 100 MeV protons at the Los Alamos National Laboratory's Isotope Production Facility.
The irradiation was motivated by interest in the characterization of the \ce{^{93}Nb}(p,4n)\ce{^{90}Mo} reaction as a new dosimetry standard for intermediate-energy protons.
Through this, a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 - 89.74 MeV are presented in this work, as well as 5 independent measurements of isomer branching ratios.
The cross sections were measured using the well-characterized \ce{^{nat}Al}(p,x)\ce{^{22}Na}, \ce{^{nat}Al}(p,x)\ce{^{24}Na}, \ce{^{nat}Cu}(p,x)\ce{^{56}Co}, \ce{^{nat}Cu}(p,x)\ce{^{62}Zn}, and \ce{^{nat}Cu}(p,x)\ce{^{65}Zn} monitor reactions  for accurate proton fluence measurement, with all activities quantified using high-purity germanium spectroscopy.
The measured cross sections are shown to be in excellent agreement with  literature values, and have been measured with significantly less uncertainty than previous measurements, through the use of variance minimization techniques to reduce proton energy uncertainties.
This work reports the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
Comparisons against the reaction modeling codes EMPIRE and TALYS are used to explore the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
Nb+p \sep Cu+p \sep Niobium \sep Copper\sep Aluminum \sep \ce{^{90}Mo}  \sep Nuclear cross sections \sep Proton activation \sep Proton transport \sep Stacked target activation \sep Monitor reactions \sep Monitor foils \sep Medical isotope production \sep Isomer branching ratios \sep Nuclear spin distributions  \sep MCNP \sep  LANL
